Fixing Vulnerabilities Hinders Maintainability (REG)

### 2019-05-17 paper/issre19.tex
changing path
abstract pass

\begin{abstract}
Security is a requirement of utmost importance to produce software with high
quality. However, there is still a considerable amount of zero-day
vulnerabilities being discovered, and fixed, almost weekly. We suspect that when
developers address these vulnerabilities on their code bases, they actually
affect the maintainability and, consequently, the reliability of software $-$ potentially introducing other
vulnerabilities. This paper evaluates the impact of refactorings to improve
security on the maintainability of open-source software. Maintainability is
measured based on the \emph{Better Code Hub}'s model of 10 guidelines using a
dataset including 607 security commits. Results show that fixing software
vulnerabilities hinders the maintainability of open-source software. This is
particularly the case for refactorings that address \emph{Broken Authentication
and Session Management} issues, \emph{Memory Leaks} and \emph{Denial-of-Service}
attacks. Furthermore, we conclude that changes to code bases to fix vulnerabilities
need to be performed with extra care in open-source software.
\end{abstract}

@@

There is still little information about the impact of patching vulnerabilities
in open-source software maintainability. 
% Hedegus et al.
% ($2018$)~\cite{HEGEDUS2018313}, analyzed the difference of maintainability between
% groups of refactored elements and non-refactored and conclude that the source
% code elements subjected to refactorings had significantly lower maintainability
% than the elements not modified.
\textit{Are developers affecting software
maintainability when trying to improve software security?}, it is what we want to investigate. Our suspiciousness is
that some of the patches may have a negative impact on the software maintainability and possibly even be the cause of the introduction
of new vulnerabilities $-$ harming software reliability. Therefore, in this paper we present an empirical study on the evolution of patches of vulnerabilities accross open-source software.

@@

{
  \bibliographystyle{unsrt}
  \bibliography{icpc19}
}

>>>>

\begin{abstract}
Security is a requirement of utmost importance to produce software of high
quality. However, there is still a considerable amount of zero-day
vulnerabilities being discovered, and fixed, almost weekly. We suspect that 
when developers address these vulnerabilities on their code bases, they actually
affect the maintainability and, pottentially, the reliability of software through the
introduction of other vulnerabilities. This paper evaluates the impact 
of refactorings to improve security on the maintainability of open-source software. 
Maintainability is measured based on the \emph{Better Code Hub}'s model of 10 guidelines 
using a dataset including 607 security commits. Results show that fixing software
vulnerabilities hinders the maintainability of open-source software. This is,
particularly, the case for refactorings that address \emph{Broken Authentication
and Session Management} issues, \emph{Memory Leaks} and \emph{Denial-of-Service}
attacks. Furthermore, we conclude that changes to code bases to fix vulnerabilities
need to be performed with extra care in open-source software.
\end{abstract}

@@

% Hedegus et al.
% ($2018$)~\cite{HEGEDUS2018313}, analyzed the difference of maintainability between
% groups of refactored elements and non-refactored and conclude that the source
% code elements subjected to refactorings had significantly lower maintainability
% than the elements not modified.

There is still little information about the impact of patching vulnerabilities
in open-source software maintainability. \textit{Are developers affecting software
maintainability when trying to improve software security?}, it is what we want to 
investigate. Our suspiciousness is that some of the patches may have a negative 
impact on the software maintainability and possibly even be the cause of the 
introduction of new vulnerabilities $-$ harming software reliability. Therefore, 
in this paper we present an empirical study on the evolution of patches of 
vulnerabilities accross open-source software.

@@

{
  \bibliographystyle{unsrt}
  \bibliography{issre19}
}
